Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-10-04 paper/manuscript.tex
?
propagate p-value issue changes

% Line numbering

@@

Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.56, 95\% CrI = {[}1, 7.36{]}). In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.76, 95\% CrI = {[}0.97, 10.71{]}), and standardized effect size is also substantially related to subjective replication score (OR = 4.36, 95\% CrI = {[}1.31, 16.65{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 4.45, 95\% CrI = {[}0.99, 28.08{]}; effect size OR = 13.93, 95\% CrI = {[}2.15, 131.6{]}).

We also ran models predicting our secondary outcome measures: a logistic model predicting whether the replication effect was within the prediction interval of the original effect, and a linear model predicting what the \(p\)-original was between the replication and original. Both these models had more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models). The strongest predictors for prediction interval were still within-participants designs (OR = 1.79, 95\% CrI = {[}0.83, 7.44{]}) and studies with larger effect sizes (OR = 1.17, 95\% CrI = {[}0.75, 2.57{]}).

>>>>

% Line numbering
\usepackage{lineno}
\linenumbers

@@

Within-participants designs stand out as the strongest correlate of replicability in the model with all the data (OR = 2.56, 95\% CrI = {[}1, 7.36{]}). In the model with all predictors, but less data, within-participants designs remain strong (OR = 2.84, 95\% CrI = {[}0.95, 10.9{]}), and standardized effect size is also substantially related to subjective replication score (OR = 3.32, 95\% CrI = {[}1.04, 11.99{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-participants OR = 3.7, 95\% CrI = {[}0.98, 21.2{]}; effect size OR = 7.34, 95\% CrI = {[}1.25, 48.65{]}).

We also ran models predicting our secondary outcome measures: a logistic model predicting whether the replication effect was within the prediction interval of the original effect, and a linear model predicting what the \(p\)-original was between the replication and original. Both these models had more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (see Supplement for results from all models). The strongest predictors for prediction interval were still within-participants designs (OR = 1.89, 95\% CrI = {[}0.84, 8.98{]}) and studies with larger effect sizes (OR = 1.2, 95\% CrI = {[}0.75, 2.81{]}).
